opponent modelling

### 2019-11-28 comp_model_1019.Rmd
plots

```{r}
# using some functions from the 'tidyverse' (also for me to get use to them ;-)
library(tidyr)
library(dplyr)
library(DEoptim)
#library(optimParallel)
# library(ggpubr)
# transform 'winner' variable in numeric score
dat$score <- recode(dat$winner, human = 1, tie = 0, ai = -1)
# create a new variable 'block' with round 1...25 = block 1 and round 26...50 as block 2
dat$block <- as.numeric(cut(dat$round,2))
# create a new data.frame in a 'wide format'
# widedata <- dat %>%
#   unite(game_block,game,block) %>% # this creates a new variable which combines game and block
#     group_by(human_id,condition,game_block) %>% # let the functions know you want to separate things by ID, condition, and game_block
#       summarize(mean_score = mean(score)) %>% # compute average score (i.e wins - losses)
#         spread(game_block,mean_score) # reformat in the 'wide' format
# # save the data file as a .csv to use in e.g. SPSS
# write.csv(widedata,row.names=FALSE,file="scores_wide.csv")

@@

#Plotting the theta/eps scatter for all participants...
plot(Nbayes_par_results$theta,Nbayes_par_results$eps,xlab="Theta", ylab= "Epsilone",col = ifelse(as.character(Nbayes_par_results$condition) == "Level2",'red','green'))
# 
# write.csv(Nbayes_par_results,file="Nbayes_par_results.csv",row.names = FALSE)
# kable(Nbayes_par_results)
```

@@

Corr_Tr_model <- data.frame()
for(id in unique(dat$human_id)) {
  tdat <- subset(dat,human_id == id)
  tot_score <- sum(tdat$score)
  tot_time <- sum(tdat$human_rt)
  early_dat <- subset(tdat,between(tdat$round,2,6) & (game =="fwg" | game =="numbers") )
  tr_score <- sum(early_dat$score)
  id_results <- subset(All_results, ID == id)
  min_BIC <- apply(id_results[,c("Random_BIC","Bayes_Tr_BIC","Bayes_No_Tr_BIC","QL_BIC","QL_states_BIC","EWA_BIC","EWA_self_BIC")],1,min)

  best_model <- c("random","Bayes Tr","Bayes No Tr","QL", "QL_states","EWA","S_EWA")[apply(id_results[,c("Random_BIC","Bayes_Tr_BIC","Bayes_No_Tr_BIC","QL_BIC","QL_states_BIC","EWA_BIC","EWA_self_BIC")],1,which.min)]
  # 
  Corr_Tr_model <- rbind(Corr_Tr_model ,
                       data.frame(
                         "id" = id,
                         "condition" = dat[dat$human_id==id,"condition"][1],
                         "Early_game_score" = tr_score,
                         "Total_score" = tot_score,
                         "Best_model" = best_model,
                         "Total_time" = sum(tdat$human_rt),
                         "TR_minus_NT_BIC" = id_results[,"Bayes_Tr_BIC"] - id_results[,"Bayes_No_Tr_BIC"],
                         "Rand_minus_best_BIC" =  id_results[,"Random_BIC"] - min_BIC

@@

Corr_Tr_model$model <- recode(Corr_Tr_model$Best_model,"Bayes Tr" = "Tranfer","Bayes No Tr" = "No Transfer", .default = "Random")
model <- factor(Corr_Tr_model$model)
condition <- factor(Corr_Tr_model$condition)

@@

Bayes_only <- subset(Corr_Tr_model, model != "Random" )

group_by(Bayes_only, model) %>%
  summarise(
    count = n(),
    mean = mean(Early_game_score, na.rm = TRUE),
    sd = sd(Early_game_score, na.rm = TRUE)
  )

wilcox.test(Early_game_score ~ model, data = Bayes_only) 
```

@@

wilcox.test(Early_game_score ~ model, data = Bayes_only)

>>>>

```{r}
# using some functions from the 'tidyverse' (also for me to get use to them ;-)
library(tidyr)
library(dplyr)
library(DEoptim)
library(optimParallel)
library(ggpubr)
# transform 'winner' variable in numeric score
dat$score <- recode(dat$winner, human = 1, tie = 0, ai = -1)
# create a new variable 'block' with round 1...25 = block 1 and round 26...50 as block 2
dat$block <- as.numeric(cut(dat$round,2))
# create a new data.frame in a 'wide format'
# widedata <- dat %>%
#   unite(game_block,game,block) %>% # this creates a new variable which combines game and block
#     group_by(human_id,condition,game_block) %>% # let the functions know you want to separate things by ID, condition, and game_block
#       summarize(mean_score = mean(score)) %>% # compute average score (i.e wins - losses)
#         spread(game_block,mean_score) # reformat in the 'wide' format
# # save the data file as a .csv to use in e.g. SPSS
# write.csv(widedata,row.names=FALSE,file="scores_wide.csv")

@@

#Plotting the theta/eps scatter for all participants...
plot(Nbayes_par_results$theta_transfer,Nbayes_par_results$eps_transfer, xlab="Theta", ylab= "Epsilone",col = ifelse(as.character(Nbayes_par_results$condition) == "Level2",'red','green'))
# 
write.csv(Nbayes_par_results,file="Nbayes_par_results.csv",row.names = FALSE)
```

@@

Corr_Tr_model <- data.frame()
for(id in unique(dat$human_id)) {
  tdat <- subset(dat,human_id == id)
  tot_score <- sum(tdat$score)
  tot_time <- sum(tdat$human_rt)
  early_dat <- subset(tdat,between(tdat$round,2,11) & (game =="fwg"))
  #early_dat <- subset(tdat,between(tdat$round,2,6) & (game =="fwg" | game =="numbers") )
  tr_score <- sum(early_dat$score)
  id_results <- subset(All_results, ID == id)
  min_BIC <- apply(id_results[,c("Random_BIC","Bayes_Tr_BIC","Bayes_No_Tr_BIC","QL_BIC","QL_states_BIC","EWA_BIC","EWA_self_BIC")],1,min)

  best_model <- c("random","Bayes Tr","Bayes NT","QL", "QL_states","EWA","S_EWA")[apply(id_results[,c("Random_BIC","Bayes_Tr_BIC","Bayes_No_Tr_BIC","QL_BIC","QL_states_BIC","EWA_BIC","EWA_self_BIC")],1,which.min)]
  # 
  Corr_Tr_model <- rbind(Corr_Tr_model ,
                       data.frame(
                         "human_id" = id,
                         "condition" = dat[dat$human_id==id,"condition"][1],
                         "Early_game_score" = tr_score,
                         "Total_score" = tot_score,
                         "Best_model" = best_model,
                         "Total_time" = sum(tdat$human_rt),
                         "TR_minus_NT_BIC" = id_results[,"Bayes_Tr_BIC"] - id_results[,"Bayes_No_Tr_BIC"],
                         "Rand_minus_best_BIC" =  id_results[,"Random_BIC"] - min_BIC

@@

Corr_Tr_model$model <- recode(Corr_Tr_model$Best_model,"Bayes Tr" = "Tranfer","Bayes No Tr" = "No Transfer", "QL_states" = "Q_Learning",  .default = "Random")
model <- factor(Corr_Tr_model$model)
condition <- factor(Corr_Tr_model$condition)

@@

Non_Random_Only <- subset(Corr_Tr_model, model != "Random" )

group_by(Non_Random_Only, model) %>%
  summarise(
    count = n(),
    mean = mean(Early_game_score, na.rm = TRUE),
    sd = sd(Early_game_score, na.rm = TRUE)
  )

res2 <- aov(Early_game_score ~ model, data = Non_Random_Only) 
summary(res2)
TukeyHSD(res2)
```

@@
